### 2017-11-27 paper/sections/5_file-systems.tex
paper: outline for #43
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

In the previous section, we used our data management language and the Mantle
policy engine to design effective cache management strategies for a new service
and domain. In this section, we compare and contrast the policies examined for
file system metadata load balancing in~\cite{sevilla:sc15-mantle} with the ones
we designed and evaluated above for cache management in ParSplice. The
similarities show how the ``when"/``where"/``how much" abstractions, data
management language, and policy engine may be widely applicable to other data
management techniques, such as QoS, scheduling, and batching.

@@

@@

% Load balancing in FSs
The abstractions in Mantle were designed for file system metadata load
balancing across a cluster of dedicated metadata servers, where spreading
requests across servers improves performance. But another technique to reduce
request load is caching. If clients and servers maintain a consistent cache,
the client can do operations locally without contacting the metadata server.
The caches in CephFS have the same performance and utilization trade-off as
ParSplice, where large caches improve performance at the expense of a higher
memory footprint. High memory utilization is problematic when a single metadata
server maintains consistent caches with many clients.  Using cache management
policies from the previous two sections has two benefits for load balancing:
(1) increases the capacity of a single metadata server, and (2) helps identify
which parts of the cache to keep local to a server. For example, applying the
key access pattern detection algorithm from
Section~\S\ref{sec:regime-detection} to a similar file system access pattern
has the potential to identify when to migrate keys and how many keys to
migrate.

% burstiness of creates then compile
To explore this example in more detail, consider the trace of metadata requests
for compiling code in CephFS shown in Figure~\ref{fig:compile-ops}.  That trace
shows the number of file system metadata requests serviced by the metadata
server when uncompressing (\texttt{untar}), compiling (\texttt{make}), and
deleting (\texttt{rm}) the source code for the Linux kernel. If the system
knows that the job phases would progress from many creates, to many lookups, to
many deletes, then it could size its caches accordingly. For example, the file
system could cache none of the metadata from the \texttt{untar} phase and run
key access pattern detection during the \texttt{make} phase, resulting in the metadata
server/clients only caching metadata that is repeatedly used. For the job in
Figure~\ref{fig:compile-ops}, this would fill up the cache to only 20K inodes
(the unit of metadata for file systems) instead of 60K, resulting in almost
40MB of memory savings (since an inode is about
1KB\footnote{http://docs.ceph.com/docs/master/dev/mds\_internals/data-structures/})
without sacrificing performance.

@@

@@

\subsection{Other Use Cases}
% we said this is good for LB/Cache management... what about others??
% QoS: when to move clients, where to move clients, how much of the reservation to move
% Other cache management: MRU
% Scheduling: how much of a resource to allocate; more than just LRU (RAD)
%\subsection{Visualizing File System Traces like ParSplice Keyspace Traces}

>>>>

In the previous section, we used our data management language and the Mantle
policy engine to design effective cache management strategies for a new service
and domain. In this section, we compare and contrast the policies examined for
file system metadata load balancing in~\cite{sevilla:sc15-mantle} with the ones
we designed and evaluated above for cache management in ParSplice.

@@

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/trace-atime.png}\\
\caption{File system metadata reads for a Lustre trace collected at LANL. The
vertical lines are the access patterns detected by the ParSplice cache
management policy from Section~\S\ref{sec:dom-specific}.
\label{fig:trace-atime}}
\end{figure}

@@

The cache management policies we developed earlier can be used by load
balancing policies to effectively spread load across a cluster. For example,
many distributed file systems spread the hierarchical namespace across a
dedicated metadata cluster and caching policies could be used to determine what
metadata to move and when to move it. To demonstrate this idea, consider
Figure~\ref{fig:trace-atime}, where the dots are the file system metadata reads
in a 1 hour window of a 3-day Lustre namespace trace and the vertical lines are
the groups of accesses detected by our policy from
Section~\S\ref{sec:regime-detection}.  The \(x\) axis is time and the \(y\)
axis is the file ID, where the file IDs are listed in the order that they
appear in the trace.  The trace is anonymized so all file names are replaced
with a unique identifier and we do not know what clients are doing.  Although
other access pattern detection algorithms are possible, we use the one designed
for cache management in Section~\S\ref{sec:regime-detection} without
modification and it successfully detects the largest group of key accesses that
starts at time 1000 seconds and ends at time 2200 seconds. File systems that
load balance file system metadata across a cluster would want to keep metadata
in that group of key accesses on the same server to reduce RPCs.

% burstiness of creates then compile
Cache management can also increase the capacity of a single server, which
affects how load should be distributed across a cluster.  For example, CephFS
clients and servers maintain a consistent cache so that the client can do
operations locally without contacting the metadata server.  But large caches
use more memory, so having smart policies that detect key access patterns would
greatly reduce memory footprints. For example, Figure~\ref{fig:compile-ops}
shows the trace of metadata requests for compiling code in CephFS.  The \(y\)
axis is  the number of file system metadata requests serviced by the metadata
server when uncompressing (\texttt{untar}), compiling (\texttt{make}), and
deleting (\texttt{rm}) the source code for the Linux kernel. If the system
knows that the job phases would progress from many creates, to many lookups, to
many deletes, then it could size its caches accordingly. For example, the file
system could cache none of the metadata from the \texttt{untar} phase and run
key access pattern detection during the \texttt{make} phase, resulting in the
metadata server/clients only caching metadata that is repeatedly used. For the
job in Figure~\ref{fig:compile-ops}, this would fill up the cache to only 20K
inodes (the unit of metadata for file systems) instead of 60K, resulting in
almost 40MB of memory savings (since an inode is about
1KB\footnote{http://docs.ceph.com/docs/master/dev/mds\_internals/data-structures/})
without sacrificing performance.

@@

\subsection{Other Use Cases}

@@

More generally, the similarities between load balancing and cache management
show how the ``when"/``where"/``how much" abstractions, data management
language, and policy engine may be widely applicable to other data management
techniques, such as:

\begin{itemize}

  \item QoS: when to move clients, where to move clients, how much of the
reservation to move

  \item Scheduling: how much of a resource to allocate; more than just LRU
(RAD)

  \item Batching: how many operations to group together and when to send large
batches of updates

  \item Prefetching: how much to prefetch and how to select data to reterive
(forward/backward/stride detection algorithms for prefetching,

\end{itemize}
